Moral Foundations of U.S. Political News Organizations: A Replication and Methodological Study

### 2024-11-30 manuscript_version/revision/revision_letter.Rmd
fixing a few typos in the response letter

Dear Dr. Editor,

Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_. Because we made a large number of changes to the document as requested, we do not copy all the changes here, but note a few specific areas. We believe the manuscript is much improved and thank the reviewers for their thoughtful commments.

@@

@@

We have streamlined in method sections when it was repetitive refering back to previous studies. We did keep places in which analyses were different or otherwise it was necessary for clarity (given the other reviewers comments).

>>>>

Dear Dr. Elson,

Thank you very much for taking the time to consider our manuscript for publication at _`r rmarkdown::metadata$journal`_. Because we made a large number of changes to the document as requested, we do not copy all the changes here, but note a few specific areas. We believe the manuscript is much improved and thank the reviewers for their thoughtful comments.

@@

Preprint: https://osf.io/rmj73/

OSF: https://osf.io/5kpj7/, https://osf.io/rmj73/

@@

We have streamlined in method sections when it was repetitive referring back to previous studies. We did keep places in which analyses were different or otherwise it was necessary for clarity (given the other reviewers comments).
